Market Expectations and Mangerial Turnover

### 2024-02-29 paper.qmd
some updates to descriptive statistics

```{r}
library(readxl)
spells1 = read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
lspells2 = read_csv("raw_data/club_manager_histories_df.csv")
skimr::skim(spells_raw)
```

>>>>

```{r}
library(dplyr)
library(purrr)
spells <- read.csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
# Define season_to_date() function here
season_to_date <- function(season) {
  if (is.na(season) | length(gsub("/", "", season)) == 0) {
    return(NA_real_)
  }

  parts <- strsplit(season, "/")[[1]]
  month <- as.numeric(parts[2])
   if (month < 8) {
     year <- paste0("20", substr(parts[1], 1, 2))
   } else {
     year <- paste0("19", substr(parts[1], 1, 2))
   }

  date_str <- paste0("01/08/", year)
  as.Date(paste(date_str, collapse = "/"), "%d/%m/%Y")
}

data_helper <- spells1 |>
  mutate(row_id=row_number()) |>
  filter(is.na(Finish)&contract_expiry!="-") |>
  select(contract_expiry, Finish,row_id)
data_helper$Finish<-as.Date(map_dbl(data_helper$contract_expiry, season_to_date))
spells |>
  mutate(row_id=row_number()) |>
  left_join(data_helper, by="row_id") |>
  mutate(Start = as.Date(Start),
         Finish = as.Date(Finish)) |>
  mutate(days_in_charge = as.numeric(Finish - Start)) ->spells

```{python}
import pandas as pd
import time
from transformers import pipeline

generator = pipeline("text-generation")
# Load model directly
# from transformers import AutoTokenizer, AutoModelForCausalLM
# 
# tokenizer = AutoTokenizer.from_pretrained("mistralai/Mixtral-8x7B-Instruct-v0.1")
# model = AutoModelForCausalLM.from_pretrained("mistralai/Mixtral-8x7B-Instruct-v0.1")  
# Use a pipeline as a high-level helper
#from transformers import pipeline
#pipe = pipeline("text-generation", model="mistralai/Mixtral-8x7B-Instruct-v0.1")

# Load the unique club names from the CSV file
spells1 = pd.read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
club_names=spells1['club'].unique()

# Initialize an empty list to store the results
results = []

# Iterate over the array of club names and add a timer for each iteration
start_time = time.time()
for club in club_names:
    # Prepare the prompt for the model
    prompt = f"Provide information about the soccer club {club}: its country of origin,  division level, and whether it is a first  team or a youth team."

    # Generate the response using the model
    start = time.time()
    responses=generator(prompt)

    # Assuming the first (or only) response is what we're interested in
    response_text = responses[0]

    # Store the response, elapsed time for this iteration and total elapsed time in our results list
    results.append({'ClubName': club, 'Information': response_text, 'ElapsedTimePerIteration': time.time() - start, 
'TotalElapsedTime': time.time() - start_time})

# Convert the results list to a DataFrame
import pandas as pd
results_df = pd.DataFrame(results)

# Display the DataFrame to verify the results
print(results_df)

# Specify the file path for the CSV file
csv_file_path = 'soccer_clubs_information_hf.csv'

# Save the DataFrame to a CSV file
results_df.to_csv(csv_file_path, index=False)

print(f"Results have been saved to {csv_file_path}")
